Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
More conclusion

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

@@

\section{Conclusions}
We have developed a trans-dimensional Bayesian approach motivated directly by
the question of whether dark substructures exist in a lens galaxy, given image
data. By making use of the Diffusive Nested Sampling algorithm \citep{dnest}
and the {\tt RJObject} library \citep{rjobject}, we outsource the difficulties
associated with choosing Metropolis proposals for a hierarchical model of
non-fixed dimension. The model allows for source and lens ``blobs'' to appear
as needed to explain the data.

>>>>

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

@@

\section{Conclusions}
We have developed a trans-dimensional Bayesian approach motivated directly by
the question of whether dark substructures exist in a lens galaxy, given image
data. By making use of the Diffusive Nested Sampling algorithm \citep{dnest}
and the {\tt RJObject} library \citep{rjobject}, we outsource the difficulties
associated with choosing Metropolis proposals for a hierarchical model of
non-fixed dimension. The model allows for source and lens ``blobs'' to appear
as needed to explain the data. The prior for the blobs' properties is
specified hierarchically, to more realistically model sensible prior beliefs,
and to tie the model parameters directly to questions of scientific interest
such as the mass function of substructures.

As a proof of concept, we demonstrated the successful recovery of a single
substructure from simulated data for which all of the model assumptions were
true. We then applied the method to an image of the Cosmic Horseshoe system
and found mild evidence in favour of the existence of a substructure, or at
the very least, a departure from a simple SIE+$\gamma$ lens profile.
